---
title: "Full Presentation Title"
subtitle: "A Comparison of Output Formats"
author: "Thomas Philip Heyes"
institute: "Faculty of Social Studies, Masaryk University"
date: today
format:
  beamer:
    theme: MU
    themeoptions:
      - workplace=fss
    aspectratio: 169
    pdf-engine: pdflatex
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{tikz}
        % Rearranged mubeamer footline: page number first (bottom left),
        % then author - title - date; MUNI FSS wordmark bottom right.
        \makeatletter
        % Suppress the infolines headline (section name at the top of slides)
        \setbeamertemplate{headline}{}
        \setbeamertemplate{footline}{%
          \hskip\mubeamer@length@margin
          \usebeamercolor[fg]{page number in head/foot}%
            \usebeamerfont{author in head/foot}\insertframenumber\ /
            \inserttotalframenumber
          \usebeamercolor[fg]{structure}%
            \usebeamerfont{structure}\ \lower2pt\hbox{\Large$\cdot$}\
          \usebeamercolor[fg]{author in head/foot}%
            \usebeamerfont{author in head/foot}\insertshortauthor
          \usebeamercolor[fg]{structure}%
            \usebeamerfont{structure}\ \lower2pt\hbox{\Large$\cdot$}\
          \usebeamercolor[fg]{title in head/foot}%
            \usebeamerfont{title in head/foot}\insertshorttitle
          \usebeamercolor[fg]{structure}%
            \usebeamerfont{structure}\ \lower2pt\hbox{\Large$\cdot$}\
          \usebeamercolor[fg]{date in head/foot}%
            \usebeamerfont{date in head/foot}\insertshortdate
          \hfill
          \hskip\mubeamer@length@margin
          \vrule width 0pt height \mubeamer@length@footlineheight
                 depth \mubeamer@length@footlinebottompadding
          \begin{tikzpicture}[remember picture,overlay]
            \node[anchor=south east,xshift=-0.25cm,yshift=0.18cm]
              at (current page.south east)
              {\includegraphics[height=0.6cm]{mubeamer/logo/mubeamer-fss-english-color}};
          \end{tikzpicture}}
        \makeatother
---

## Bullet Points

Plain text, **bold text**, *italic text*, and `inline code`.

- A single-line bullet list item
- A bullet list item that is quite long in order to force a line break,
  which also contains **emphasized text**
  - A second-level list item
    - A third-level list item
  - A second-level item with a math expression $E = mc^2$

1. A numbered list item
2. Another numbered list item

## A Table

| First Name | Surname  | Field      | Nobel Prize |
|------------|----------|------------|:-----------:|
| Albert     | Einstein | Physics    |    1921     |
| Marie      | Curie    | Chemistry  |    1911     |
| Ivan       | Pavlov   | Physiology |    1904     |

: The great minds of the turn of the century

## Table from an R Data Frame (kable)

```{r}
#| echo: false
#| message: false
library(dplyr)
mtcars |>
  group_by(cyl) |>
  summarise(
    n = n(),
    mpg = mean(mpg),
    hp = mean(hp),
    wt = mean(wt)
  ) |>
  knitr::kable(
    digits = 1, booktabs = TRUE,
    col.names = c("Cylinders", "N", "Mean MPG", "Mean HP", "Mean weight"),
    caption = "mtcars summarised by cylinder count (dplyr + kable)"
  )
```

## Styled Table (kableExtra)

```{r}
#| echo: false
#| message: false
#| warning: false
library(kableExtra)
mtcars |>
  head(6) |>
  select(mpg, cyl, hp, wt) |>
  kbl(
    format = "latex", booktabs = TRUE, digits = 2,
    col.names = c("MPG", "Cylinders", "HP", "Weight"),
    caption = "First six rows of mtcars (kableExtra styling)"
  ) |>
  kable_styling(latex_options = "striped") |>
  row_spec(0, bold = TRUE, color = "white", background = "#0000DC")
```

## A Figure

```{r}
#| echo: false
#| fig-cap: "Simulated treatment effect by experimental group"
#| fig-width: 7
#| fig-height: 4
#| out-height: 55%
library(ggplot2)
set.seed(42)
d <- data.frame(
  group = rep(c("Control", "Treatment A", "Treatment B"), each = 50),
  outcome = c(rnorm(50, 5.0, 1.2), rnorm(50, 5.8, 1.2), rnorm(50, 6.4, 1.2))
)
ggplot(d, aes(group, outcome)) +
  geom_boxplot(fill = "#0000DC", alpha = 0.15, colour = "#0000DC") +
  labs(x = NULL, y = "Outcome score") +
  theme_minimal(base_size = 14)
```

## Annotated Figure (ggplot + ggforce)

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-cap: "Highlight box, arrow, and explanatory textbox drawn in code"
#| fig-width: 8
#| fig-height: 4.2
#| out-height: 55%
library(ggforce)
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(colour = "#0000DC", size = 2.5) +
  geom_mark_rect(
    aes(filter = wt > 5, label = "Heavy cars"),
    description = "These three drag the trend line down",
    fill = "#FBAE40", alpha = 0.2, colour = "#F08C00",
    label.fontsize = c(11, 9)
  ) +
  annotate("curve",
    x = 2.3, y = 14.5, xend = 3.4, yend = 15.2,
    curvature = 0.25, colour = "grey30",
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("label",
    x = 2.3, y = 13.5, label = "A manual annotate() label\nwith an arrow",
    size = 3.2, fill = "white"
  ) +
  labs(x = "Weight (1000 lbs)", y = "Miles per gallon") +
  theme_minimal(base_size = 14)
```

## Two Columns

:::: {.columns}

::: {.column width="45%"}
- Point about the figure
- Another observation
- A third, longer remark that wraps
  onto a second line
:::

::: {.column width="55%"}
```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 4
barplot(
  c(23, 41, 17, 35),
  names.arg = c("Q1", "Q2", "Q3", "Q4"),
  col = "#0000DC", border = NA,
  ylab = "Respondents"
)
```
:::

::::

# A Section Heading

{{< include _contact.qmd >}}
